Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-12 MS/ms.Rmd
Fixed word rendering of equation, finally.

Assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone - CORT) on reproduction [e.g., see @Podmola2018]. We might extract data from studies manipulating corticosterone in bird eggs. Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species. If the studies are experimental in nature than a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable. We then might fit an overall multilevel meta-analytic model as follows: 
$$
Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i}\ \\
a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}\textbf{A}), \\
sp_{k[i]}\sim N(0, \sigma^{2}_{species}\textbf{I}), \\
s_{j[i]}\sim N(0, \sigma^{2}_{study}\textbf{I}), \\
e_{i}\sim N(0, \sigma^{2}_{residual}\textbf{I}), \\
m_{i} \sim N(0, v_{i}\textbf{I}) \\
$$

>>>>

Assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone - CORT) on reproduction [e.g., see @Podmola2018]. We might extract data from studies manipulating corticosterone in bird eggs. Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species. If the studies are experimental in nature than a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable. We then might fit an overall multilevel meta-analytic model as follows: 
$$
\begin{split}
Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} \\
a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}\textbf{A}), \\
sp_{k[i]}\sim N(0, \sigma^{2}_{species}\textbf{I}), \\
s_{j[i]}\sim N(0, \sigma^{2}_{study}\textbf{I}), \\
e_{i}\sim N(0, \sigma^{2}_{residual}\textbf{I}), \\
m_{i} \sim N(0, v_{i}\textbf{I}) \\
\end{split}
$$
